---
title: "Crag_pheno_match"
author: "Me"
date: "1/18/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

rm(list=ls())

```{r}
#load necassary libraries, need bioconductor installed
library(ape)
library(phytools)
library(geiger)
#library(OUwie)
```

```{r}
#read in initial phylogeny from MrBayes and parse data 
cragphy<-read.tree("Crangonyctidae_13.nex")  
cragdat<-read.table("matched.txt", header=T)
tmp<-treedata(cragphy, cragdat, sort=T) # useful function in geiger that creates an object with the overlapping taxa in the tree and the dataset
tr<-tmp[[1]]
dat<-tmp[[2]]
plot(cragphy)

#write.tree(tr, file = "species_mito.tre")
plot(tr)

#phylogenetic signal 
phytools::phylosig(tr, dat[,1], method="lambda")
phytools::phylosig(tr, dat[,3], method="lambda")
phytools::phylosig(tr, dat[,4], method="lambda")
phytools::phylosig(tr, dat[,5], method="lambda")
```

```{r}
#phylogenetic regressions and model selection

library(phylolm)

BM_means=phylolm(dat[,1]~dat[,4], phy=tr, model="BM")
#summary(BM_means)
BM_CVs=phylolm(dat[,3]~dat[,6], phy=tr, model="BM")
summary(BM_CVs)

OU_means=phylolm(dat[,1]~dat[,4], phy=tr, model="OUrandomRoot")
#summary(OU_means)
OU_CVs=phylolm(dat[,3]~dat[,6], phy=tr, model="OUrandomRoot")
summary(OU_CVs)

mod1 = lm(dat[,3]~dat[,6])
summary(mod1)

library(MuMIn)
model.sel(BM_means, OU_means, mod1)
model.sel(BM_CVs, OU_CVs)
#qqnorm(mod1$residuals)
#qqnorm(mod2$residuals)
```


```{r}
# We will first use the node height test on independent contrasts to determine if the rate of photophobia is speeding up or slowing down over time 

# First estimate the log of female length at sexual maturity (1st column) and log body mass (2nd column) 

#logflsm<-log10(dat[,2])
behCV = dat[,3]
beh =  dat[,1]

#logmass<-log10(dat[,1])
respCV = dat[,6]
resp = dat[,4]

picbehavCV<-pic(behCV, tr)
picrespCV<-pic(respCV, tr)

picbehav<-pic(beh, tr)
picresp<-pic(resp, tr)

plot(picbehav, picresp)
plot(beh ~ resp, cragdat)

plot(picbehavCV, picrespCV)
plot(beh_CV ~ resp_CV, cragdat)
```

```{r}
#Now run a regression through the origin for the contrasts (signs of contrasts are arbitrary therefore regression needs to be through the origin)

picCV<-lm(picbehavCV ~ 0 + picrespCV)
pic<-lm(picbehav ~ 0 + picresp)
summary(picCV)
summary(pic)
```

```{r}
behCV.NH<-nh.test(tr, behCV, regression.type="lm", show.plot=TRUE) # the other option is a robust regression, which can be very useful see Slater & Pennell 2013 syst. biol.
behCV.NH
```

######## Model fitting ########
```{r}
# We will now use model-fitting to determine if photophobia is best fit by a Brownian motion model, a model that allows the rate to speed up or slow down over time or a non-phylogenetic white noise model that assumes a single normal distribution of the data with no phylogenetic covariance amongst species. We will use the fitContinuous function in geiger for these models and AIC to identify the best-fitting model. When using the Akaike Information Criterion (corrected for small sample size AICc) the rule of thumb is a difference between the best fitting model (the lowest AICc score) which is referred to as the deltaAIc of 2 or more suggest some support for one model over another and >10 is substantial support. 

behCV.BM<-fitContinuous(tr, behCV, model="BM")
behCV.WN<-fitContinuous(tr, behCV, model="white")
behCV.EB<-fitContinuous(tr, behCV, model="EB") 

# We can compare these models most easily using AIC (or the small-sample corrected AICc). AIC is an 'information criterion' that weights the fit of the model against the number of parameters in the model to help us measure the strength of evidence for each model. Lower AIC values indicate better evidence for a given model. We can also compute the AIC-weights - which essentially standardizes the AIC scores of fitted alternative models to measure the relative weight of evidence for each model in our data.

aic.vals<-setNames(c(behCV.BM$opt$aicc, behCV.WN$opt$aicc, behCV.EB$opt$aicc),
    c("BM","WN","EB"))
lnL.vals<-setNames(c(behCV.BM$opt$lnL, behCV.WN$opt$lnL, behCV.EB$opt$lnL),
    c("BM","WN","EB"))
lnL.vals
aic.vals
aic.w(aic.vals)


#Brownian is the winner!!!
```

```{r}
beh.BM<-fitContinuous(tr, beh, model="BM")
beh.WN<-fitContinuous(tr, beh, model="white")
beh.EB<-fitContinuous(tr, beh, model="EB") 

lnL.vals<-setNames(c(beh.BM$opt$lnL, beh.WN$opt$lnL, beh.EB$opt$lnL),
    c("BM","WN","EB"))
lnL.vals

aic.vals<-setNames(c(beh.BM$opt$aicc, beh.WN$opt$aicc, beh.EB$opt$aicc),
    c("BM","WN","EB"))
aic.vals
aic.w(aic.vals)

#white noise is the winner!!!
```

```{r}
respCV.BM<-fitContinuous(tr, respCV, model="BM")
respCV.WN<-fitContinuous(tr, respCV, model="white")
respCV.EB<-fitContinuous(tr, respCV, model="EB") 

lnL.vals<-setNames(c(respCV.BM$opt$lnL, respCV.WN$opt$lnL, respCV.EB$opt$lnL),
    c("BM","WN","EB"))
lnL.vals

aic.vals<-setNames(c(respCV.BM$opt$aicc, respCV.WN$opt$aicc, respCV.EB$opt$aicc),
    c("BM","WN","EB"))
aic.vals
aic.w(aic.vals)

#white noise is the winner!!!
```

```{r}
resp.BM<-fitContinuous(tr, resp, model="BM")
resp.WN<-fitContinuous(tr, resp, model="white")
resp.EB<-fitContinuous(tr, resp, model="EB") 

lnL.vals<-setNames(c(resp.BM$opt$lnL, resp.WN$opt$lnL, resp.EB$opt$lnL),
    c("BM","WN","EB"))
lnL.vals

aic.vals<-setNames(c(resp.BM$opt$aicc, resp.WN$opt$aicc, resp.EB$opt$aicc),
    c("BM","WN","EB"))
aic.vals
aic.w(aic.vals)

#white noise is the winner!!!
```

######## Repeated with ultrametric tree #########

```{r}
# make ultrametric tree 
cragphy<-read.tree("Crangonyctidae_13.nex")  
cragdat<-read.table("matched.txt", header=T)
ultraphy = force.ultrametric(cragphy, method=c("nnls","extend"))
tmp<-treedata(ultraphy, cragdat, sort=T) # useful function in geiger that creates an object with the overlapping taxa in the tree and the dataset
tr<-tmp[[1]]
dat<-tmp[[2]]
```

```{r}
behCV.BM<-fitContinuous(tr, behCV, model="BM")
behCV.WN<-fitContinuous(tr, behCV, model="white")
behCV.EB<-fitContinuous(tr, behCV, model="EB") 

aic.vals<-setNames(c(behCV.BM$opt$aicc, behCV.WN$opt$aicc, behCV.EB$opt$aicc),
    c("BM","WN","EB"))
aic.vals
aic.w(aic.vals)

#Brownian is the winner!!!
```


```{r}
beh.BM<-fitContinuous(tr, beh, model="BM")
beh.WN<-fitContinuous(tr, beh, model="white")
beh.EB<-fitContinuous(tr, beh, model="EB") 

aic.vals<-setNames(c(beh.BM$opt$aicc, beh.WN$opt$aicc, beh.EB$opt$aicc),
    c("BM","WN","EB"))
aic.vals
aic.w(aic.vals)

#white noise is the winner!!!
```

```{r}
respCV.BM<-fitContinuous(tr, respCV, model="BM")
respCV.WN<-fitContinuous(tr, respCV, model="white")
respCV.EB<-fitContinuous(tr, respCV, model="EB") 

aic.vals<-setNames(c(respCV.BM$opt$aicc, respCV.WN$opt$aicc, respCV.EB$opt$aicc),
    c("BM","WN","EB"))
aic.vals
aic.w(aic.vals)

#white noise is the winner!!!
```

```{r}
resp.BM<-fitContinuous(tr, resp, model="BM")
resp.WN<-fitContinuous(tr, resp, model="white")
resp.EB<-fitContinuous(tr, resp, model="EB") 

aic.vals<-setNames(c(resp.BM$opt$aicc, resp.WN$opt$aicc, resp.EB$opt$aicc),c("BM","WN","EB"))
aic.vals
aic.w(aic.vals)

#white noise is the winner!!!
```
####### ultrametric produced essentially the same results so we can just use the original #######

```{r}
#write.tree(tr, file = "species_mito_ultra.tre")
plot(tr)
```

######## Repeat with habitat tree #########

```{r}
#read in habitat trees
mito.tr<-read.tree("species_mito.tre") 
habA.tr<-read.tree("species_habitat_Aa.tre")
habB.tr<-read.tree("species_habitat_B.tre")
hab_poly.tr<-read.tree("species_habitat_poly.tre")

plot(mito.tr)
plot(habA.tr)
plot(habB.tr)
plot(hab_poly.tr)
is.binary.tree(habA.tr)
is.binary.tree(habB.tr)

tr<-tmp[[1]] #this is from the above
tr1 = habA.tr
tr2 = habB.tr
```

######### Topology 1 #########
######### the CV crap is nonsense outside of the phylo lm ########

```{r}
beh.BM<-fitContinuous(tr, beh, model="BM")
beh.WN<-fitContinuous(tr, beh, model="white")
beh.BM.hab<-fitContinuous(tr1, beh, model="BM") 

lnL.vals<-setNames(c(beh.BM$opt$lnL, beh.WN$opt$lnL, beh.BM.hab$opt$lnL),
    c("BM","WN","hab"))
lnL.vals

aic.vals<-setNames(c(beh.BM$opt$aicc, beh.WN$opt$aicc, beh.BM.hab$opt$aicc),
    c("BM","WN","hab"))
aic.vals
aic.w(aic.vals)

#BM is the winner!!!
```

```{r}
resp.BM<-fitContinuous(tr, resp, model="BM")
resp.WN<-fitContinuous(tr, resp, model="white")
resp.BM.hab<-fitContinuous(tr1, resp, model="BM") 

lnL.vals<-setNames(c(resp.BM$opt$lnL, resp.WN$opt$lnL, resp.BM.hab$opt$lnL),
    c("BM","WN","hab"))
lnL.vals

aic.vals<-setNames(c(resp.BM$opt$aicc, resp.WN$opt$aicc, resp.BM.hab$opt$aicc),c("BM","WN","hab"))
aic.vals
aic.w(aic.vals)

#WN is the winner!!!
```

######### Topology 2 #########

```{r}
beh.BM<-fitContinuous(tr, beh, model="BM")
beh.WN<-fitContinuous(tr, beh, model="white")
beh.BM.hab<-fitContinuous(tr2, beh, model="BM") 

aic.vals<-setNames(c(beh.BM$opt$aicc, beh.WN$opt$aicc, beh.BM.hab$opt$aicc),
    c("BM","WN","hab"))
aic.vals
aic.w(aic.vals)

#BM is the winner!!!
```

```{r}
resp.BM<-fitContinuous(tr, resp, model="BM")
resp.WN<-fitContinuous(tr, resp, model="white")
resp.BM.hab<-fitContinuous(tr2, resp, model="BM") 

aic.vals<-setNames(c(resp.BM$opt$aicc, resp.WN$opt$aicc, resp.BM.hab$opt$aicc),c("BM","WN","hab"))
aic.vals
aic.w(aic.vals)

#WN is the winner!!!
```

************************
ANSs
************************

```{r fig.height=2, fig.width=3}
#All rates different habitat
pdf(file = "ANS_habitat.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

hab = setNames(this[,1],rownames(this))

plotTree(tree, fsize=1, ftype="i", lwd=1, offset=1)

cols = setNames(c("darkseagreen", "indianred1", "gray35"),levels(hab))

tiplabels(pie=to.matrix(hab[tree$tip.label],
    levels(hab)),piecol=cols,cex=1)

fitARD = ace(hab, tree, model="ARD", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.5,
    y=5.5,fsize=0.5)

dev.off()
```


```{r fig.height=2, fig.width=3}
#All rates different behavior 
pdf(file = "ANS_behavior.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

pheno = setNames(this[,2],rownames(this))

plotTree(tree, fsize=1, ftype="i", lwd=1, offset=1)

cols = setNames(c("gray35", "indianred1"),levels(pheno))

tiplabels(pie=to.matrix(pheno[tree$tip.label],
    levels(pheno)),piecol=cols,cex=1)

fitARD = ace(pheno, tree, model="ARD", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.5,
    y=5.5,fsize=0.5)

dev.off()
```

```{r fig.height=1, fig.width=2}
#All rates different respiratory 
pdf(file = "ANS_respiratory.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

pheno = setNames(this[,6],rownames(this))

plotTree(tree, fsize=1, ftype="i", lwd=1, offset=1)

cols = setNames(c("gray35", "indianred1"),levels(pheno))

tiplabels(pie=to.matrix(pheno[tree$tip.label],
    levels(pheno)),piecol=cols,cex=1)

fitARD = ace(pheno, tree, model="ER", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.5,
    y=5.5,fsize=0.5)

dev.off()
```

##### With contor colors #####

```{r fig.height=2, fig.width=3}
#All rates different behavior 
pdf(file = "ANS_behavior_contMap.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

pheno = setNames(this[,2],rownames(this))

this2 = read.csv("matched_beh.csv", row.names=1, stringsAsFactors = TRUE)

dat = as.matrix(this2)[,1]

fit<-fastAnc(tree,dat,vars=TRUE,CI=TRUE)

n<-length(obj$cols)
obj<-contMap(tree,dat,plot=FALSE)
obj$cols[1:n]<-colorRampPalette(c("black","red"), space="Lab")(n)
plot(obj, offset=1, lwd=3,
    outline=FALSE,legend=FALSE)

cols = setNames(c("gray35", "indianred1"),levels(pheno))

fitARD = ace(pheno, tree, model="ER", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

tiplabels(pie=to.matrix(pheno[tree$tip.label],
    levels(pheno)),piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.5,
    y=5.5,fsize=0.5)

dev.off()
```

```{r fig.height=2, fig.width=3}
#All rates different repiratory 
pdf(file = "ANS_resp_contMap.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

pheno = setNames(this[,6],rownames(this))

this2 = read.csv("matched_resp.csv", row.names=1, stringsAsFactors = TRUE)

dat = as.matrix(this2)[,1]

fit<-fastAnc(tree,dat,vars=TRUE,CI=TRUE)

n<-length(obj$cols)
obj<-contMap(tree,dat,plot=FALSE)
obj$cols[1:n]<-colorRampPalette(c("gray5","red"), space="Lab")(n)
plot(obj, offset=1, lwd=3,
    outline=FALSE,legend=FALSE)

cols = setNames(c("gray35", "indianred1"),levels(pheno))

fitARD = ace(pheno, tree, model="ER", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

tiplabels(pie=to.matrix(pheno[tree$tip.label],
    levels(pheno)),piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.5,
    y=5.5,fsize=0.5)

dev.off()
```

```{r fig.height=2, fig.width=3}
#All rates different behavior 
pdf(file = "ANS_hab_beh_contMap.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

hab = setNames(this[,1],rownames(this))

this2 = read.csv("matched_beh.csv", row.names=1, stringsAsFactors = TRUE)

dat = as.matrix(this2)[,1]

fit<-fastAnc(tree,dat,vars=TRUE,CI=TRUE)

n<-length(obj$cols)
obj<-contMap(tree,dat,plot=FALSE)
obj$cols[1:n]<-colorRampPalette(c("gray5","red"), space="Lab")(n)
plot(obj, offset=1, lwd=3,
    outline=FALSE,legend=FALSE)

cols = setNames(c("darkseagreen", "indianred1", "gray35"),levels(hab))

fitARD = ace(hab, tree, model="ARD", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

tiplabels(pie=to.matrix(hab[tree$tip.label],
    levels(hab)),piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.525,
    y=5.5,fsize=0.5)

add.color.bar(0.15, obj$cols,title="behavior",
    lims=obj$lims,digits=2,prompt=FALSE,x=0.525,
    y=4,lwd=3,fsize=0.5,subtitle="", outline=FALSE)

dev.off()
```

```{r fig.height=2, fig.width=3}
#All rates different behavior 
pdf(file = "ANS_hab_resp_contMap.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

hab = setNames(this[,1],rownames(this))

this2 = read.csv("matched_resp.csv", row.names=1, stringsAsFactors = TRUE)

dat = as.matrix(this2)[,1]

fit<-fastAnc(tree,dat,vars=TRUE,CI=TRUE)

n<-length(obj$cols)
obj<-contMap(tree,dat,plot=FALSE)
obj$cols[1:n]<-colorRampPalette(c("gray5","red"), space="Lab")(n)
plot(obj, offset=1, lwd=3,
    outline=FALSE,legend=FALSE)

cols = setNames(c("darkseagreen", "indianred1", "gray35"),levels(hab))

fitARD = ace(hab, tree, model="ARD", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

tiplabels(pie=to.matrix(hab[tree$tip.label],
    levels(hab)),piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.525,
    y=5.5,fsize=0.5)

add.color.bar(0.15, obj$cols,title="respiratory",
    lims=obj$lims,digits=2,prompt=FALSE,x=0.525,
    y=4,lwd=3,fsize=0.5,subtitle="", outline=FALSE)

dev.off()
```

```{r fig.height=2, fig.width=3}
#All rates different behavior 
pdf(file = "ANS_resp_contMap.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

pheno = setNames(this[,6],rownames(this))

this2 = read.csv("matched_resp.csv", row.names=1, stringsAsFactors = TRUE)

dat = as.matrix(this2)[,1]

fit<-fastAnc(tree,dat,vars=TRUE,CI=TRUE)


obj<-contMap(tree,dat,plot=FALSE)
n<-length(obj$cols)
obj$cols[1:n]<-colorRampPalette(c("gray5","red"), space="Lab")(n)
plot(obj, offset=1, lwd=3,
    outline=FALSE,legend=FALSE)

cols = setNames(c("gray5", "red"),levels(pheno))

#fitARD = ace(hab, tree, model="ARD", type="discrete")

#nodelabels(node=1:tree$Nnode+Ntip(tree), pie=fitARD$lik.anc,piecol=cols,cex=1)

tiplabels(pie=to.matrix(pheno[tree$tip.label],
    levels(pheno)),piecol=cols,cex=1)

#add.simmap.legend(colors=cols,prompt=FALSE,x=0.525,y=5.5,fsize=0.5)

add.color.bar(0.15, obj$cols,title="respiratory",
    lims=obj$lims,digits=2,prompt=FALSE,x=0.525,
    y=4,lwd=3,fsize=0.5,subtitle="", outline=FALSE)

dev.off()
```

```{r fig.height=2, fig.width=3}
#All rates different behavior 
pdf(file = "ANS_beh_contMap.pdf", width = 3, height = 2)

tree = tr

this = read.csv("matched.csv", row.names=1, stringsAsFactors = TRUE)

pheno = setNames(this[,2],rownames(this))

this2 = read.csv("matched_beh.csv", row.names=1, stringsAsFactors = TRUE)

dat = as.matrix(this2)[,1]

fit<-fastAnc(tree,dat,vars=TRUE,CI=TRUE)


obj<-contMap(tree,dat,plot=FALSE)
n<-length(obj$cols)
obj$cols[1:n]<-colorRampPalette(c("gray5","red"), space="Lab")(n)
plot(obj, offset=1, lwd=3,
    outline=FALSE,legend=FALSE)

cols = setNames(c("gray5", "red"),levels(pheno))

#fitARD = ace(hab, tree, model="ARD", type="discrete")

#nodelabels(node=1:tree$Nnode+Ntip(tree), pie=fitARD$lik.anc,piecol=cols,cex=1)

tiplabels(pie=to.matrix(pheno[tree$tip.label],
    levels(pheno)),piecol=cols,cex=1)

#add.simmap.legend(colors=cols,prompt=FALSE,x=0.525,y=5.5,fsize=0.5)

add.color.bar(0.15, obj$cols,title="respiratory",
    lims=obj$lims,digits=2,prompt=FALSE,x=0.525,
    y=4,lwd=3,fsize=0.5,subtitle="", outline=FALSE)

dev.off()
```

pheno = setNames(this[,3],rownames(this))

plotTree(tree, fsize=1, ftype="i", lwd=1, offset=1)

cols = setNames(c("gray35", "indianred1"),levels(pheno))

tiplabels(pie=to.matrix(pheno[tree$tip.label],
    levels(pheno)),piecol=cols,cex=1)

fitARD = ace(pheno, tree, model="ARD", type="discrete")

nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD$lik.anc,piecol=cols,cex=1)

add.simmap.legend(colors=cols,prompt=FALSE,x=0.5,
    y=5.5,fsize=0.5)

#dev.off()
```

************************
Phylomorphos
************************

```{r fig.height=3, fig.width=3}
#get tree ordered correctly to match data
crag.tree = read.tree("Crangonyctidae_13.nex")  
cragdat<-read.csv("matched.csv", header=T)
#Matching tree and data with fish data
matched<-make.treedata(crag.tree,cragdat)
#matched
crag.td <- reorder(matched, "postorder")
#summary(td) 
#phytools::phylosig(fish.td$phy, fish.td[['haploid']]) #measures phylogenetic signal 
crag.td$phy
```

```{r fig.height=3, fig.width=3}
#CVs
tree=crag.td$phy
cent=read.csv("phylomorph_CV.csv")
X=as.matrix(cent)
phylomorphospace(tree,X,xlab="Respiratory CV",ylab="Behavior CV", label=FALSE, colors=cols,lwd=2, xlim=c(0.05, 0.35), ylim=c(0.05, 0.3))

  #or
 
phylomorphospace(tree,X,xlab="Respiratory CV",ylab="Behavior CV",label="radial", colors=cols,lwd=2, xlim=c(0, 0.4), ylim=c(0.05, 0.3))

  #or 
 
phylomorphospace(tree,X,xlab="Respiratory CV",ylab="Behavior CV",label=FALSE, colors=cols,lwd=2, xlim=c(0, 0.4), ylim=c(0, 0.3))
```


```{r fig.height=3, fig.width=3}
#phenotype
tree=crag.td$phy
cent=read.csv("phylomorph_phen.csv")
X=as.matrix(cent)
phylomorphospace(tree,X,xlab="Respiratory",ylab="Behavior",label="horizontal", colors=cols,lwd=2, xlim=c(0.3, 0.8), ylim=c(0.4, 0.85))

  #or
 
phylomorphospace(tree,X,xlab="Respiratory",ylab="Behavior",label="radial", colors=cols,lwd=3)

  #or 
 
phylomorphospace(tree,X,xlab="Respiratory",ylab="Behavior",label=FALSE, colors=cols,lwd=2, xlim=c(0.42, 0.7), ylim=c(0.4, .85))
```

```{r fig.height=3, fig.width=6}
phylomorphospace(tree,X,xlab="Respiratory CV",ylab="Behavior CV",label=FALSE, colors=cols,lwd=2)
```
